---
title: "National Pride Revisited"
author: "Ian Scot Nesbitt, M.A."
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

```{r Libraries}
library(tidyverse)
library(lmSupport)
library(countrycode)
library(stringr)
library(psych)
library(GPArotation)
library(lme4)
library(lm.beta)
library(stargazer)
library(xtable)

#Uninstall lmerTest due to incompatibilty with stargazer
#detach("package:lmerTest", unload = TRUE)
```

```{r Read National Identity Data (raw data is exported from STATA 14 .dta format into a .csv format)}
d <- read.csv("/Users/ianscotnesbitt/Documents/ISN Data/ISSP raw data.csv")
# link to raw data for download: https://www.gesis.org/issp/modules/issp-modules-by-topic/national-identity/2013/
```

```{r Country Codes}
# Relabeling countries according to their ISO 3 character code.
d$country <- as.factor(countrycode(d$V4, origin = 'iso3n', destination = 'iso3c'))

# Relabeling the variable that distinguishes key regions within countries, like East and West Germany.
d$country.region <- d$C_ALPHAN

# Checking that country codes have been matched correctly.
unique(d[, c("V4", "country", "country.region")])
# Recoding is correct.
```

```{r National Pride Item Recoding}
# Creating dependent variables for each of the 12 pride items.
d$pride.overall <- d$V58                # Overall National Pride
d$pride.internationalsports <- d$V22    # Pride in International Sports
d$pride.democracy <- d$V25              # Pride in Democracy
d$pride.influence <- d$V26              # Pride in Level of Global Influence
d$pride.economy <- d$V27                # Pride in Economic Achievements
d$pride.welfare <- d$V28                # Pride in Welfare State  
d$pride.science <- d$V29                # Pride in Scientific and Technological Achievements
d$pride.sports <- d$V30                 # Pride in Sports
d$pride.arts <- d$V31                   # Pride in Arts
d$pride.military <- d$V32               # Pride in Military
d$pride.history <- d$V33                # Pride in History
d$pride.fairness <- d$V34               # Pride in Level of Fair Treatment of all Groups in Society

# Survey Labels:
# Very proud = 1
# Somewhat proud = 2
# Not very proud = 3
# Not proud at all = 4

# Recoding pride items on a 0 to 100 scale.
d <- d %>%
  mutate_at(
    c(
    "pride.overall",
    "pride.democracy",
    "pride.influence",
    "pride.economy",
    "pride.welfare",
    "pride.science",
    "pride.sports",
    "pride.arts",
    "pride.military",
    "pride.history",
    "pride.fairness"
      ),
    funs(
      recode(.,
             '1'=100,
             '2'=67,
             '3'=33,
             '4'=0))) %>% mutate_at(
               c(    "pride.overall",
                     "pride.democracy",
                     "pride.influence",
                     "pride.economy",
                     "pride.welfare",
                     "pride.science",
                     "pride.sports",
                     "pride.arts",
                     "pride.military",
                     "pride.history",
                     "pride.fairness"),
               funs(recode(.,
             '1'=100,
             '2'=67,
             '3'=33,
             '4'=0)))
             


# Survey Labels:
# Agree strongly = 1
# Agree = 2
# Neither agree nor disagree = 3
# Disagree = 4
# Disagree strongly = 5

# Recoding of pride in international sports due to the item having a different initial scale. 
d$pride.internationalsports <- recode(d$pride.internationalsports,
                                      '1'=100,
                                      '2'=75,
                                      '3'=50,
                                      '4'=25,
                                      '5'=0
                                      )

# Checking that pride items are correctly recoded in terms of values and class.
table(d$pride.overall, d$V58)
str(d$pNatlQ)
# Recoding is correct

table(d$pride.internationalsports, d$V22)
str(d$pride.internationalsports)
# Recoding is correct

table(d$pride.democracy, d$V25)
str(d$pride.democracy)
# Recoding is correct

table(d$pride.influence, d$V26)
str(d$pride.influence)
# Recoding is correct

table(d$pride.economy, d$V27)
str(d$pride.economy)
# Recoding is correct

table(d$pride.welfare, d$V28)
str(d$pride.welfare)
# Recoding is correct

table(d$pride.science, d$V29)
str(d$pride.science)
# Recoding is correct

table(d$pride.sports, d$V30)
str(d$pride.sports)
# Recoding is correct

table(d$pride.arts, d$V31)
str(d$pride.arts)
# Recoding is correct

table(d$pride.military, d$V32)
str(d$pride.military)
# Recoding is correct

table(d$pride.history, d$V33)
str(d$pride.history)
# Recoding is correct

table(d$pride.fairness, d$V34)
str(d$pride.fairness)
# Recoding is correct
```

```{r Sex}
# Recoding and refactoring sex.

# Survey Labels:
# Male = 1
# Female = 2

d$sex <- recode(d$SEX,
                  '1'="Male",
                  '2'="Female")

d$sex <- as.factor(d$sex)

# Checking that sex is recoded correctly in terms of values and class.
table(d$sex, d$SEX)
str(d$sex)
# Recoding is correct
```

```{r Citizenship}
# Recoding citizenship status.

# Survey Labels:
# Yes = 1
# No = 2

d$citizenship <- recode(d$V63, 
                     '1'="Citizen", 
                     '2'="Non-Citizen"
                     )
d$citizenship <- as.factor(d$citizenship)

# Checking that citizenship is recoded correctly in terms of values and class.
table(d$citizenship, d$V63)
str(d$citizenship)
# Recoding is correct
```

```{r Rurality}
# Recoding place of living as urban = 0 and rural = 1.

# Survey Labels:
# A big city = 1 
# The suburbs or outskirts of a big city = 2
# A town or a small city = 3
# A country village = 4
# A farm or home in the country = 5

d$community <- recode(d$URBRURAL, 
                   '1'="Big City", 
                   '2'="Suburbs", 
                   '3'="Town",
                   '4'="Village", 
                   '5'="Country"
                   )
d$community <- as.factor(d$community)

# Checking that rurality is recoded correctly in terms of values and class.
table(d$community, d$URBRURAL)
str(d$community)
# Recoding is correct
```

```{r Education}
# Recoding years of education. 95 is still in HS, 96 is still in college. 
d$EDUCYRS <- as.numeric(d$EDUCYRS)
d$education <- recode(d$EDUCYRS, 
                   '95'=11, 
                   '96'=14
                   )

# Recoding values of years of education greater than 25 to NA.
d$education <- ifelse(d$education < 26, d$education, NA)

# Histogram of years of education.
hist.education <- ggplot(d, aes(x=education)) + 
  geom_histogram(color="black",
                 fill="blue",
                 na.rm=TRUE, 
                 binwidth=2) +
  labs(title="Histogram of Years of Education",
       x="Years", 
       y="Number of Respondents") +
  theme_dark()
hist.education
```
###NOTE: Need to improve imputation of 95 (still in HS) and 96 (still in college) -- consider using age and highest degree to pick a more accurate number.
```{r Age}
# Recoding of Age to include only adults.
d$AGE <- as.numeric(d$AGE)
d$age <- ifelse(d$AGE >= 18 & d$AGE < 999, d$AGE, NA)

# Creating quadratically transformed age variable.
d$age.quadratic <- (d$age)^2

# Creating Age variable for participants between 18 and 75 years old.
d$age.lessthan75 <- ifelse(d$age > 75, NA, d$age)

# 2013 Age of respondents who were born at the time communism fell.
d$age.born1989 <- as.factor(ifelse(d$age > 24, "Born Before Fall", "Born After Fall"))
d$age.born1989 <- fct_relevel(d$age.born1989, "Born Before Fall")

# 2013 Age of respondents who were 18 at the time communism fell.
d$age.adult1989 <- as.factor(ifelse(d$age > 42, "Adult Before Fall", "Adult After Fall"))
d$age.adult1989 <- fct_relevel(d$age.adult1989, "Adult Before Fall")

# Histogram of Age
hist.age <- ggplot(d, aes(x=age)) + 
  geom_histogram(color="black",
                 fill="red",
                 na.rm=TRUE, 
                 binwidth=5) +
  labs(title="Histogram of Age",
       x="Pride (0-100)", 
       y="Number of Respondents") +
  theme_dark()
hist.age
```

```{r Religiosity}
# Recoding religious attendance to reflect amount of times one attends per year.

# Survey Labels:
# Several times a week or more often = 8 
# Once a week = 7 
# 2 or 3 times a month = 6
# Once a month  = 5
# Several times a year = 4 
# Once a year = 3
# Less frequently than once a year = 2
# Never = 1

d$attend.religious <- recode(d$ATTEND,
                             '8'=100,
                             '7'=50,
                             '6'=30,
                             '5'=12,
                             '4'=6,
                             '3'=1,
                             '2'=.5,
                             '1'=.01
                             )

d$attend.religious <- as.numeric(d$attend.religious)

# Histogram of Religiosity
hist.attend.religious <- ggplot(d, aes(x=attend.religious)) + 
  geom_histogram(color="black",
                 fill="yellow",
                 na.rm=TRUE, 
                 binwidth=15) +
  labs(title="Histogram of Yearly Religious Attendance",
       x="Attendances (0-100)", 
       y="Number of Respondents") +
  theme_dark()
hist.attend.religious
```

```{r Ex-Communist Countries and Regions}
# Creating a dummy variable to represent whether a country has a communist history or not.

# List of Ex-Communist countries:
# Czech Republic
# East Germany
# Estonia
# Georgia
# Croatia
# Hungary
# Lithuania
# Latvia
# Russia
# Slovenia
# Slovakia


d$economic.system <- ifelse(
    d$country.region == "CZ"|
    d$country.region == "DE-E"| 
    d$country.region == "EE"|
    d$country.region == "GE"|
    d$country.region == "HR"|
    d$country.region == "HU"|
    d$country.region == "LT"|
    d$country.region == "LV"|
    d$country.region == "RU"|
    d$country.region == "SI"|
    d$country.region == "SK",
    "Communist",
    "Market"
    )
d$economic.system <- as.factor(d$economic.system)

# Checking that ex-communist societies are correctly coded in terms of values and class.
xt.econ.system <- unique(subset(d, select = c("country.region", "economic.system")))
xt.econ.system
# Recoding is correct.
```

```{r Nordic Countries}
# Creating a dummy variable to represent whether a country is Nordic or not.

# List of Nordic countries:
# Denmark
# Finland
# Iceland
# Norway
# Sweden

d$nordic <- d$country.region
d$nordic <- ifelse(
    d$country.region == "DK"|
    d$country.region == "FI"|
    d$country.region == "IS"|
    d$country.region == "NO"|
    d$country.region == "SE",
    "Nordic",
    "Non-Nordic"
    )
d$nordic <- as.factor(d$nordic)

# Checking that Nordic societies are correctly coded in terms of values and class.
xt.nordic <- unique(subset(d, select = c("country.region", "nordic")))
xt.nordic
# Coding is correct.
```

```{r Read 2013 GDP Per Capita and Population Data}
IMFd <- read.csv("/Users/ianscotnesbitt/Documents/ISN Data/IMF raw data.csv", stringsAsFactors = FALSE)
# Download link to raw GDP Per Capita data: https://www.imf.org/external/pubs/ft/weo/2018/02/weodata/index.aspx

# Steps to download GDP per capita and population data from the International Monetary Fund:

# Select "By Countries (country-level data)"
# 1. Select "All countries."
# 2. Select "Continue."
# 3. Select "Gross domestic product, current prices - Purchasing power parity; international dollars."
# 3. Select "Population."
# 4. Select 2013 for "Start Year" and "End Year."
# 4. Select "ISO Alpha-3 Code" and "Subject Descriptor" for "Fields to show on report." 
# 4. Leave all other default options, e.g. decimal formatting.
# 4. Select "Prepare Report"
# 5. Navigate to the bottom of the page and download Microsoft Excel file with IMF data.
```

```{r Cleaning IMF Data}
# Removing extra rows that only contain an auto-inserted description of the data from IMF.
IMFd <- IMFd[-c(389, 390),]

# Concatenating the units and scales so that they do not get lost in translation during data transposition.
IMFd$UnitScale <- paste0(IMFd$Units, IMFd$Scale)

# Reducing data to necessary columns.
IMFd <- IMFd[, c("ISO", "UnitScale", "X2013")]

# Transposing data from long to wide form.
IMFd <- spread(IMFd, UnitScale, X2013)

# Renaming columns containing GDP per capita and population data.
names(IMFd)[2:3] <- c("population.millions", "gdp.ppp")
```

```{r GDP per Capita at Purchasing Power Parity}
# Matching GDP per capita data to appropriate countries in original national identity data.
d$gdp <- IMFd$gdp.ppp[match(d$country, IMFd$ISO)]

# Recoding GDP per capita data into correct class.
d$gdp <- as.numeric(gsub(",", "", d$gdp))

# Checking that GDP per capita data is matched to the appropriate countries.
unique(d[, c("country", "gdp")])
# Matching is correct.

# Dividing GDP per capita by 1000 so that regression estimates are more meaningful.
d$gdp.1k <- d$gdp/1000
```

```{r Population in millions of people}
# Matching population data to appropriate countries in original national identity data.
d$population <- IMFd$population.millions[match(d$country, IMFd$ISO)]

# Recoding population data into correct class.
d$population <- as.numeric(gsub(",", "", d$population))

# Checking that population data is matched to the appropriate countries.
unique(d[, c("country", "population")])
#Matching is correct.

# Creating logarithmically transformed population variable.
d$population.log <- log10(d$population)

# Creating quadratically transformed population variable.
d$population.quadratic <- (d$population)^2
```

```{r Pre-factor analysis correlations}
# Generating correlations among pride items and other criterion variables to see what items might work together in scales.
# Items should be correlated together, and should have similar correlations with other variables to be considered for items.

# Correlations among the pride items.
PRIDEd <- subset(d, select=c(pride.overall:pride.fairness))
cor.pride <- round(cor(PRIDEd, use = "complete.obs"),3)
cor.pride[upper.tri(cor.pride)] <- ""
cor.pride <- as.data.frame(cor.pride)
cor.pride

# Write out for inclusion in the paper.
#write.table(cor.pride, "/Users/ianscotnesbitt/Desktop/National Pride Project/Excel Files/Tables/Pride Correlations.csv", sep = ",", row.names = TRUE, col.names = TRUE)

# Correlations among the pride items and years of education.
EDd <- subset(d, select=c(pride.overall:pride.fairness, education))
cor.ed <- round(cor(EDd, use = "complete.obs"),3)
cor.ed[upper.tri(cor.ed)] <- ""
cor.ed <- as.data.frame(cor.ed)
cor.ed

# Correlations among the pride items and church attendance.
RELIGIONd <- subset(d, select=c(pride.overall:pride.fairness, attend.religious))
cor.reli <- round(cor(RELIGIONd, use = "complete.obs"),3)
cor.reli[upper.tri(cor.reli)] <- ""
cor.reli <- as.data.frame(cor.reli)
cor.reli

# Correlations among the pride items and age.
AGEd <- subset(d, select=c(pride.overall:pride.fairness, age))
cor.age <- round(cor(AGEd, use = "complete.obs"),3)
cor.age[upper.tri(cor.age)] <- ""
cor.age <- as.data.frame(cor.age)
cor.age
```

```{r National Pride Item Factor Analysis}
# Dataframe for factor analysis of pride items that does NOT include pNatlQ, overall national pride.
PRIDEd2 <- subset(PRIDEd, select=c(pride.internationalsports:pride.fairness))

# Generating scree plot and suggested nunber of factors.
parallel <- fa.parallel(PRIDEd2, fm = 'ml', fa = 'fa')

# Factor analysis with 4 factors, varimax rotation, and maximum liklihood factor extraction method.
PRIDE.fa <- fa(PRIDEd2, nfactors = 2, rotate = "varimax", fm="ml")
PRIDE.fa

PRIDEd2 %>% head(., 50) %>% View

# Write out for inclusion in the paper.
#write.table(round(loadings(PRIDE.fa),3), "/Users/ianscotnesbitt/Desktop/National Pride Project/Excel Files/Tables/Pride Factor Analysis.csv", sep = ",", row.names = TRUE, col.names = TRUE)
```
###INTERPRETATION: The above factor analysis suggests that pride.democracy, pride.economy, pride.influence, pride.welfare, could form a scale related to advancement/development, and that pride.arts and pride.sports could form another related to leisure/recreation. Next, I will see how these items are correlated with other variables. They should all have very similar correlations with the other variables if they are measuring the same construct. 
```{r Post-Factor Analysis Correlations - Advancement Items}
# Testing correlations of pride.democracy, pride.economy, pride.influence and pride.welfare with other criterion variables.
ADVANCEMENTd <- subset(d,
                       select=c(pride.democracy,
                                pride.economy,
                                pride.influence,
                                pride.welfare,
                                education,
                                age,
                                attend.religious,
                                gdp,
                                population
                                )
                       )

cor.adv <- round(cor(ADVANCEMENTd, use = "complete.obs"),3)
cor.adv[upper.tri(cor.adv)] <- ""
cor.adv <- as.data.frame(cor.adv)
cor.adv

# Get omega
alpha.adv <- omega(ADVANCEMENTd[,c("pride.democracy", "pride.economy", "pride.welfare")])
alpha.adv
```
###INTERPRETATION: based on this correlation table, I feel confident to include pride.democracy, pride.economy and pride.welfare in a scale, but pride.influence deviates a bit too much and does not offer quite as much face validity.
```{r Pride in Advancement Scale}
# Creating scale for pride in country's advancement/development
d$pride.advancement <- (d$pride.democracy + d$pride.economy + d$pride.welfare)/3

# Histogram of pAdvQ
hist.advancement <- ggplot(d, aes(x=pride.advancement)) + 
  geom_histogram(color="black",
                 fill="orange",
                 na.rm=TRUE, 
                 binwidth=11) +
  labs(title="Histogram of Pride in Country's Advancement",
       x="Pride (0-100)", 
       y="Number of Respondents") +
  theme_dark()
hist.advancement
```

```{r Post-Factor Analysis Correlations - Leisure Items}
# Testing correlations of pArtsQ and pSportQ with other criterion variables.
LEISUREd <- subset(d,
                    select=c(pride.arts,
                             pride.sports,
                             education,
                             age,
                             attend.religious,
                             gdp,
                             population
                                )
                       )

cor.leis <- round(cor(LEISUREd, use = "complete.obs"),3)
cor.leis[upper.tri(cor.leis)] <- ""
cor.leis <- as.data.frame(cor.leis)
cor.leis
```
###INTERPRETATION: Based on my factor analysis, pArtsQ and pSportQ load heavily onto factor 2.The above correlation table also reveals that they share very similar correlations with a range of other criterion variables, so I am comfortable making a scale with them, despite only having two items.
```{r Pride in Leisure Activities Scale}
# Creating scale for pride in country's leisure/recreation.
d$pride.leisure <- (d$pride.arts + d$pride.sports)/2

# Histogram of pLeisQ
hist.leisure <- ggplot(d, aes(x=pride.leisure)) +
  geom_histogram(color="black",
                 fill="green",
                 na.rm=TRUE,
                 binwidth=12) +
  labs(title="Histogram of Pride in Country's Leisure Activities",
       x="Pride (0-100)",
       y="Number of Respondents") +
  theme_dark()
hist.leisure
```

```{r Means and SDs of Overall National Pride, Pride in Advancement, and Pride in Leisure Activities by Country}
descriptives.dvs <- d %>%
  group_by(country) %>%
  summarize_at(vars("pride.overall",
                    "pride.advancement",
                    "pride.leisure"),
               funs(mean(., na.rm=TRUE),
                    sd(., na.rm=TRUE))) %>%
  rename("Country" = country,
         "Overall Pride Mean" = pride.overall_mean,
         "Pride in Advancement Mean" = pride.advancement_mean,
         "Pride in Leisure Mean" = pride.leisure_mean,
         "Overall Pride SD" = pride.overall_sd,
         "Pride in Advancement SD" = pride.advancement_sd,
         "Pride in Leisure SD" = pride.leisure_sd) %>% 
  select("Country",
         "Overall Pride Mean",
         "Overall Pride SD",
         "Pride in Advancement Mean",
         "Pride in Advancement SD",
         "Pride in Leisure Mean",
         "Pride in Leisure SD") %>% 
  mutate_if(is.numeric, round, 3)

# Write out the table for inclusion in the paper.
#write.table(descriptives.dvs, "/Users/ianscotnesbitt/Desktop/National Identity/Excel Files/Tables/Outcome Variable Descriptives by Country.csv", sep = ",", row.names = FALSE, col.names = TRUE)
```

```{r Frequency of each Survey Response for Overall Natioanl Pride by Country}
d$pride.overall.f <- recode(d$pride.overall,
                            `0` = "Not proud at all",
                            `33` = "Not very proud",
                           `67` =  "Somewhat proud",
                            `100` = "Very proud",
                           .missing = "Missing") %>% 
fct_relevel(., "Missing", after = Inf)

# Create row-wise frequencies by factor-level by country excluding NAs
tbl.op1 <- d %>% filter(pride.overall.f != "Missing") %>% 
  count(country, pride.overall.f) %>%
  group_by(country) %>%
  mutate(prop = round(prop.table(n),2)) %>%
  select(-n) %>%
  pivot_wider(names_from = pride.overall.f, values_from = prop)

# Create column-wise frequencies of NAs only
tbl.op2 <- d %>% filter(pride.overall.f == "Missing") %>% 
  group_by(country) %>%
  summarise (n = n()) %>%
  mutate(Missing = round(n / sum(n),2)) %>%
  select(-n)

# Bind row-wise frequencies of valid cases with frequencies of NAs
tbl.op.c <- merge(tbl.op1, tbl.op2, by = "country")

View(tbl.op.c)


# write out tables for paper
#write.table(tbl.op1, "/Users/ianscotnesbitt/Desktop/National Identity/Excel Files/Tables/Overall NP by Country.csv", sep = ",", row.names = FALSE, col.names = TRUE)
write.table(tbl.op.c, "/Users/ianscotnesbitt/Desktop/National Identity/Excel Files/Tables/Overall NP by Country.csv", sep = ",", row.names = FALSE, col.names = TRUE)
```

```{r OLS Regression Model of Overall National Pride on Individual Criterion Variables}
ols.np <- lm(pride.overall ~
               education +
               age +
               sex +
               citizenship +
               attend.religious +
               community,
             data = d
             )
lm.beta(ols.np)
summary(ols.np)
```

```{r Multilevel Regression Model of Overall National Pride on Individual and Contextual Criterion Variables}
ml.np <- lmer(pride.overall ~
                education +
                age +
                sex +
                citizenship +
                attend.religious +
                community +
                economic.system +
                gdp.1k +
                population +
                (1|country),
              data = d
              )
summary(ml.np)
```

```{r Multilevel Regression Models of Overall National Pride with Age*Ex-Communist Interaction}
ml.np.int1 <- lmer(pride.overall ~
                     education +
                     age +
                     sex +
                     citizenship +
                     attend.religious +
                     community +
                     economic.system +
                     gdp.1k +
                     population +
                     economic.system*age +
                     (1|country),
                   data = d
                  )

ml.np.int2 <- lmer(pride.overall ~
                     education +
                     age +
                     sex +
                     citizenship +
                     attend.religious +
                     community +
                     economic.system +
                     gdp.1k +
                     population +
                     economic.system*age.born1989 +
                    (1|country),
                  data = d
                  )

ml.np.int3 <- lmer(pride.overall ~
                     education +
                     age +
                     sex +
                     citizenship +
                     attend.religious +
                     community +
                     economic.system +
                     gdp.1k +
                     population +
                    economic.system*age.adult1989 +
                    (1|country),
                  data = d
                  )

summary(ml.np.int1)
summary(ml.np.int2)
summary(ml.np.int3)
```

#INTERPRETATION: Significant interactions in all three models.

```{r Overall National Pride Regression Table}
stargazer(ols.np,
          ml.np,
          ml.np.int1,
          ml.np.int2,
          ml.np.int3,
          title="Overall National Pride Regression Table",
          dep.var.labels =c("Overall National Pride"),
          covariate.labels=c("Education",
                             "Age",
                             "Male",
                             "Non-Citizen",
                             "Church Attendance",
                             "Countryside",
                             "Suburbs",
                             "Town",
                             "Village",
                             "Market",
                             "GDP per capita",
                             "Population",
                             "Market*Age",
                             "Born before 1989",
                             "Market*Born before 1989",
                             "Adult before 1989",
                             "Market*Adult before 1989"),
          align = TRUE,
          single.row = TRUE,
          type = 'text')
```

```{r Age Ex-Communist on Overall National Pride Among People 18 to 75}
# Continuous age variable.
np.int.plot1 <- ggplot(data = d,
                       aes(x = age.lessthan75,
                           y = pride.overall,
                           group = economic.system,
                           color = economic.system)) +
  geom_smooth(method = "lm") +
  xlab("Age") +
  ylab("Overall National Pride") +
  theme(legend.title = element_blank())
np.int.plot1

# Categorical age variable, born before or after 1989.
np.int.plot2 <- ggplot(data = subset(d, !is.na(age.born1989)),
                       aes(x = age.born1989,
                           y = pride.overall,
                           group = economic.system,
                           color = economic.system)) +
  geom_smooth(method = "lm") +
  xlab("Age") +
  ylab("Overall National Pride") +
  theme(legend.title = element_blank())
np.int.plot2

# Categorical age variable, adult before or after 1989.
np.int.plot3 <- ggplot(data = subset(d, !is.na(age.adult1989)),
                       aes(x = age.adult1989,
                           y = pride.overall,
                           group = economic.system,
                           color = economic.system)) +
  geom_smooth(method = "lm") +
  xlab("Age") +
  ylab("Overall National Pride") +
  theme(legend.title = element_blank())
np.int.plot3
```

```{r OLS Regression Model of Pride in Advancement on Individual Criterion Variables}
ols.adv <- lm(pride.advancement ~
               education +
               age +
               sex +
               citizenship +
               attend.religious +
               community,
              data = d
              )
lm.beta(ols.adv)
summary(ols.adv)
```

```{r Multilevel Regression Model of Pride in Advancement on Individual and Contextual Criterion Variables}
ml.adv <- lmer(pride.advancement ~
                 education +
                 age +
                 sex +
                 citizenship +
                 attend.religious +
                 community +
                 economic.system +
                 gdp.1k +
                 population +
                 (1|country),
               data = d
               )
summary(ml.adv)
```

```{r Multilevel Regression Models of Pride in Advancement with Age*Ex-Communist Interaction}
ml.adv.int1 <- lmer(pride.advancement ~
                      education +
                      age +
                      sex +
                      citizenship +
                      attend.religious +
                      community +
                      economic.system +
                      gdp.1k +
                      population +
                      economic.system*age +
                      (1|country),
                    data = d
                    )
summary(ml.adv.int1)

ml.adv.int2 <- lmer(pride.advancement ~
                       education +
                       age +
                       sex +
                       citizenship +
                       attend.religious +
                       community +
                       economic.system +
                       gdp.1k +
                       population +
                       economic.system*age.born1989 +
                       (1|country),
                     data = d
                     )
summary(ml.adv.int2)

ml.adv.int3 <- lmer(pride.advancement ~
                       education +
                       age +
                       sex +
                       citizenship +
                       attend.religious +
                       community +
                       economic.system +
                       gdp.1k +
                       population +
                       economic.system*age.adult1989 +
                    (1|country),
                  data = d
                  )
summary(ml.adv.int3)
```
#INTERPRETATION: Significant Interaction.
```{r Pride in Advancement Regression Table}
stargazer(ols.adv,
          ml.adv,
          ml.adv.int1,
          ml.adv.int2,
          ml.adv.int3,
          title="Pride in Advancement Regression Table",
          dep.var.labels =c("Pride in Advancement"),
          covariate.labels=c("Education",
                             "Age",
                             "Male",
                             "Non-Citizen",
                             "Church Attendance",
                             "Countryside",
                             "Suburbs",
                             "Town",
                             "Village",
                             "Market",
                             "GDP per capita",
                             "Population",
                             "Market*Age",
                             "Born before 1989",
                             "Market*Born before 1989",
                             "Adult before 1989",
                             "Market*Adult before 1989"),
          align = TRUE,
          single.row = TRUE,
          type = 'text')
```

```{r Age by Ex-Communist on Pride in Advancement Among People 18 to 75}
adv.int.plot1 <- ggplot(data = d, aes(x = age.lessthan75,
                                      y = pride.advancement,
                                      group = economic.system,
                                      color = economic.system)) +
  geom_smooth(method = "lm") +
  xlab("Age") +
  ylab("Advancement National Pride") +
  theme(legend.title = element_blank())
adv.int.plot1

adv.int.plot2 <- ggplot(data = subset(d, !is.na(age.born1989)),
                         aes(x = age.born1989,
                             y = pride.advancement,
                             group = economic.system,
                             color = economic.system)) +
  geom_smooth(method = "lm") +
  xlab("Age") +
  ylab("Advancement National Pride") +
  theme(legend.title = element_blank())
adv.int.plot2

adv.int.plot3 <- ggplot(data = subset(d, !is.na(age.adult1989)),
                         aes(x = age.adult1989,
                             y = pride.advancement,
                             group = economic.system,
                             color = economic.system)) +
  geom_smooth(method = "lm") +
  xlab("Age") +
  ylab("Advancement National Pride") +
  theme(legend.title = element_blank())
adv.int.plot3
```

```{r OLS Regression Model of Pride in Leisure Activities on Individual Criterion Variables}
ols.leis <- lm(pride.leisure ~
                 education +
                 age +
                 sex +
                 citizenship +
                 attend.religious +
                 community,
               data = d
               )
lm.beta(ols.leis)
summary(ols.leis)
```

```{r Multilevel Regression Model of Pride in Leisure Activities on Individual and Contextual Criterion Variables}
ml.leis <- lmer(pride.leisure ~
                  education +
                  age +
                  sex +
                  citizenship +
                  attend.religious +
                  community +
                  economic.system +
                  gdp.1k +
                  population +
                  (1|country),
                data = d
                )
summary(ml.leis)
```

```{r Multilevel Regression Model of The Components of Leisure Activities Scale on Individual and Contextual Criterion Variables}
# Pride in sports
ml.sport <- lmer(pride.sports ~
                  education +
                  age +
                  sex +
                  citizenship +
                  attend.religious +
                  community +
                  economic.system +
                  gdp.1k +
                  population +
                  (1|country),
                data = d
                )
summary(ml.sport)

#Pride in arts
ml.art <- lmer(pride.arts ~
                  education +
                  age +
                  sex +
                  citizenship +
                  attend.religious +
                  community +
                  economic.system +
                  gdp.1k +
                  population +
                  (1|country),
                data = d
                )
summary(ml.art)

# Pride in international sports
ml.intsport <- lmer(pride.internationalsports ~
                      education +
                      age +
                      sex +
                      citizenship +
                      attend.religious +
                      community +
                      economic.system +
                      gdp.1k +
                      population +
                      (1|country),
                    data = d
                )
summary(ml.intsport)
```
#INTERPRETATION: We suspected that education might predict pride in sports differently than pride in arts, and these models confirm this. Education predicts lower pride in sports and higher pride in arts. I then regress pride in international sports on education and find the same pattern as with sports in general: education predicts lower pride.
```{r Multilevel Regression Models of Pride in Leisure Activities with Age*Ex-Communist Interaction}
ml.leis.int1 <- lmer(pride.leisure ~
                     education +
                       age +
                       sex +
                       citizenship +
                       attend.religious +
                       community +
                       economic.system +
                       gdp.1k +
                       population +
                       economic.system*age +
                     (1|country),
                   data = d
                   )
summary(ml.leis.int1)

ml.leis.int2 <- lmer(pride.leisure ~
                     education +
                       age +
                       sex +
                       citizenship +
                       attend.religious +
                       community +
                       economic.system +
                       gdp.1k +
                       population +
                       economic.system*age.born1989 +
                     (1|country),
                  data = d
                  )
summary(ml.leis.int2)

ml.leis.int3 <- lmer(pride.leisure ~
                     education +
                       age +
                       sex +
                       citizenship +
                       attend.religious +
                       community +
                       economic.system +
                       gdp.1k +
                       population +
                       economic.system*age.adult1989 +
                     (1|country),
                  data = d
                  )
summary(ml.leis.int3)
```
#INTERPRETATION: Non-significant Interaction. No need to plot the lines.
```{r Pride in Leisure Activities Regression Table}
stargazer(ols.leis,
          ml.leis,
          ml.leis.int1,
          ml.leis.int2,
          ml.leis.int3,
          title="Pride in Leisure Activities",
          dep.var.labels =c("Pride in Leisure Activites"),
          covariate.labels=c("Education",
                             "Age",
                             "Male",
                             "Non-Citizen",
                             "Church Attendance",
                             "Countryside",
                             "Suburbs",
                             "Town",
                             "Village",
                             "Market",
                             "GDP per capita",
                             "Population",
                             "Market*Age",
                             "Born before 1989",
                             "Market*Born before 1989",
                             "Adult before 1989",
                             "Market*Adult before 1989"),
          align = TRUE,
          single.row = TRUE,
          type = 'text')
```
